---
title: "Group Challenge Problems"
output: html_notebook
---

#Challenge #1

###Problem
1. Produce a vector of files in a folder of your chosing on your comptuer.
2. Find the size of each file.
3. Provide a vector that sorts the files from largest to smallest.  

* You can ignore folders and files inside of subfolders.
* When you run list.files(), without paramaters, what do you see.
* What kind of object does list.files return?

###Hints

> setwd(...) allows us to programtically set our working directory

> list.files(...) gets a list of file names

> file.size(...) get the size of a file.

#Challenge #2

R contains hundreds of built in datasets for you to play with.  These can be very helpful while learning.

```{r}
LETTERS
datasets::discoveries
```

You can learn more about a dataset by running:
```{r}
help(discoveries)
```
Take note of what is included in the data dictionary.

Let's make it "rain" with the precip dataset.  Start by reading about it:
```{r}
help(precip)
```

Now, create a single vector, rain, that contains 3 elements.
* The sum of the average rainfall for states with less than 25 inches of rain.
* The sum of the average rainfall for states with more than 25 inches of rain and less than 40 inches of rain.
* The sum of the average rainfall for states with more than 39 inches of rain.

```{r}

```

#Challenge #3

###Problem
Let's create a big dataset to test the performance of vectorization of functions.  

* Create a vector that has a length of 9,000,000.  
* Each element should be an alternating character following the pattern: A B C A B C ...
* Name that vector "bigdata"

> bigdata <- ?

Good job.  Unfortunatly, the big data police would like a change.  Please provide the following more descriptive labels
> "A" should become "Hacking Skills"

> "B" should become "Math & Stats"

> "C" should become "Domain Knowledge"

They tried to do this themselves by looping through each element (don't worry, we will cover for loops later in the class).  Unfortunatly, there solution takes too long on 9 million records.  Here is their code:

```{r}
rename = function(input_vector) {
  output_vector = input_vector
  for(index in seq_along(input_vector)) {
    if(input_vector[index] == 'A') {
      output_vector[index] = 'Text for A'
    } else if(input_vector[index] == 'B') {
      output_vector[index] = 'Text for B'
    } else if(input_vector[index] == 'C') {
      output_vector[index] = 'Text for C'
    }   
  }   
  return(output_vector)
}

bigdata_fixed <- rename(input_vector = bigdata)
```

How can we do this in a way that takes advantage of R's support for vectorization?

Vectors can really increase our performance.

###Hint
* Can the subselection function [ ] do more for us than just filter elements?